---
title: "Lab 5 Key"
author: "Alex Setmajer"
date: "10/25/2021"
output: 
  html_document: 
    theme: lumen
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message= FALSE, warning= FALSE)

library(tidyverse)
library(effsize)
```


## Part 1: Confidence Intervals
In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1
Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.

```{r}
# Create a mock sample
otter_lengths <- c(30,45,28,31,34,46,52,29,90,72,112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# Find the standard deviation:
otter_sd <- sd(otter_lengths)

```

This means that we would expect that 95% of the confidence intervals calculated would contain the true population mean.

DON'T JUST WRITE THIS:
Mean otter length is 36.7 inches with a 95% confidence interval of [29.1, 44.7] inches.

ALSO INCLUDE: (where n denotes the sample size, and the $\pm$ denotes the standard deviation
Mean otter length is 36.7 inches $\pm$ 9.3 (mean $\pm$ sd, n=8) with a 95% confidence interval of [29.1, 44.7] inches.

^^^ this is problematic because the values are typed out, so if the data changes this text is not reproducible. we want to build in ways to have the outputs of our code directly tied to text with in-line referencing. So store outcomes as something with a name.

To call elements from a list:
`objectname$valuename` for example, `otter_ci$p.value` will return the p.value... and so forth. 

#### Now, using in-line referencing
Typing `r` is like starting a mini code chunk in your text. For example:

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2],1)`] inches.

## Part 2: Two-Sample t-test

### Example 1
Make two mock samples, and ask the question: do we have sufficient evidence to make us reflect the null hypothesis that these samples were drawn from populations with the same mean?

```{r}
# Make my mock samples
oak_trees <- c(20,19,24,28,34,12,15,25)

pine_trees <- c(60,43,56,21,68,50,36,46)

# Two-sample t-test
tree_t <- t.test(oak_trees, pine_trees)

# Null hypothesis: means heights are the same
# ie.: Trees are drawn from populations with the same mean height
```
If samples were drawn from two populations with the same mean height, there is a 0.1% chance that the sample means are at least as different as this by random chance. 

^ Dont write this in a report that is just how you say it and interpret it.Instead write:

The mean heights of oak and pine trees were (X +- Y) and (X +- Y), respectively, and the difference was significant (t(`r round(tree_t$parameter, 1)`) = `r round(tree_t$statistic,1)`, p = `r round(tree_t$p.value, 3)`.

`t(df) = t-statistic, p=p-value`

*AVOID*: p = 0
When this get really small (usually p < 0.001) just write that instead of, for example, p = 0.00000003 .... its even possible to code this into the text. 

## Part 3: Another t-test with cars data

Using `mpg` dataset.

### Take a look at the data

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact", "suv"))

# check that filter worked to see what is included in the specified column
unique(compact_suv$class)

```

Create a histogram of city gas mileage (cty) faceted by class starting from compact_suv.(and a qq graph)

```{r}
ggplot(data=compact_suv, aes(x=cty)) +
  geom_histogram(bins = 12) +
    facet_wrap(~ class)

ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)
```

Find some summary statistics for each group.

```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city= round(mean(cty), 2), 
    sd_city= round(sd(cty),2),
    sample_size = n()
  )

# only round values if this were to be the final table... if you are going to do calculations from this object do not round.

car_stats
```

The t.test() function REALLY wants vectors of things. Use the `pull()` function to pull out a vector from a data frame.

Remember can look up info about a function by typing `?functionname` in the console. For example `?pull`.

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty) # this makes a vector of those values.
```

# Your turn: do the same thing to get a vector of city gas mileages for SUVs 
```{r}
suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)

```

H0 (aka null hypothesis): Mean city gas mileages for SUVs and compact cards are the same

```{r}
t.test(compact_sample, suv_sample)
```
We reject the null hypothesis that the mean city cas mileage is the same. 

There is a significant difference in mean city cas mileage for SUVs and compact cars (t(df)....
