---
title: "Lab 5 Key"
author: "Alex Setmajer"
date: "10/25/2021"
output: 
  html_document: 
    theme: lumen
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message= FALSE, warning= FALSE}
knitr::opts_chunk$set(echo = TRUE, message= FALSE, warning= FALSE)

library(tidyverse)
library(effsize)
```


## Part 1: Confidence Intervals
In this section, we'll use the `t.test()` function to calculate confidence intervals.

### Example 1
Create a single mock sample containing a number of values, then learn to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.

```{r}
# Create a mock sample
otter_lengths <- c(30,45,28,31,34,46,52,29,90,72,112)

# Find the confidence interval:
otter_ci <- t.test(otter_lengths)

# Find the standard deviation:
otter_sd <- sd(otter_lengths)

```

This means that we would expect that 95% of the confidence intervals calculated would contain the true population mean.

DON'T JUST WRITE THIS:
Mean otter length is 36.7 inches with a 95% confidence interval of [29.1, 44.7] inches.

ALSO INCLUDE: (where n denotes the sample size, and the $\pm$ denotes the standard deviation
Mean otter length is 36.7 inches $\pm$ 9.3 (mean $\pm$ sd, n=8) with a 95% confidence interval of [29.1, 44.7] inches.

^^^ this is problematic because the values are typed out, so if the data changes this text is not reproducible. we want to build in ways to have the outputs of our code directly tied to text with in-line referencing. So store outcomes as something with a name.

To call elements from a list:
`objectname$valuename` for example, `otter_ci$p.value` will return the p.value... and so forth. 

#### Now, using in-line referencing
Typing `r` is like starting a mini code chunk in your text. For example:

Mean otter length is `r round(otter_ci$estimate, 1)` inches.
